Architectures for workflow integration in science gateways

### 2016-04-15 paper.tex
Added figure on nested workflows
Updates in section 3.6

\begin{figure*}
\def\svgwidth{2\columnwidth}
\input{figures/VIP.pdf_tex}
\caption{Architecture of the Virtual Imaging Platform that integrates
  the MOTEUR workflow engine through service invocation.}
\label{fig:vip-architecture}
\end{figure*}

@@

Nested workflows have long been available in workflow engines, for
instance in the Taverna workbench~\cite{oinn2004taverna}. This model
was used by the SHIWA Simulation Platform to implement Coarse-Grained
workflow interoperability~\cite{terstyanszky2014enabling}, i.e. to
integrate various workflow engines in a consistent platform. Nested
workflows are also often used implicitly to wrap scripts as
black-boxes while these scripts actually correspond to complete workflows.

@@

@@

See Figure~\ref{archi:import}. This is an abstract model that we
instantiate with the service invocation architecture for
consistency. Workflows are integrated in the science gateway through
format conversion from a native format to the science gateway
format. This was implemented in the SHIWA Simulation Platform through
the IWIR language that provided a common language for portability
across grid workflow
systems~\cite{plankensteiner-prodan-etal:2013}.

@@

\paragraph{Scalability} As in the service architecture, adding a new
workflow instance requires manual configuration in the science gateway
(instance of a parent engine), or in the parent engine (instance of a
child engine) (\texttt{S$_1$=1}). Similarly, elastic engines are
difficult to achieve (\texttt{S$_2$=1}). Distributed engines are
possible, through meta-workflows (\texttt{S$_3$=0}). Task scheduling
is more complex than in other architectures though, due to the fact
that workflow execution is split in different engines (\texttt{S$_4$=1}).

\subsection{Workflow import with service invocation}

>>>>

\begin{figure*}
\centering
\def\svgwidth{1.5\columnwidth}
\input{figures/VIP.pdf_tex}
\caption{Architecture of the Virtual Imaging Platform that integrates
  the MOTEUR workflow engine through service invocation.}
\label{fig:vip-architecture}
\end{figure*}

@@

Nested workflows have long been available in workflow engines, for
instance in the Taverna workbench~\cite{oinn2004taverna}. They were
also used by the SHIWA Science Gateway to implement so-called
Coarse-Grained workflow
interoperability~\cite{terstyanszky2014enabling}, i.e. to integrate
various workflow engines in a consistent
platform. Figure~\ref{fig:shiwa-architecture} shows the architecture
used in the SHIWA Science Gateway for nested workflow execution. It
corresponds to the nested worfklow with service invocation in
Figure~\ref{archi:nested}. The parent workflow engine is WS-PGRADE,
invoked as a service in the Science Gateway (step \texttt{1} on
Figure~\ref{fig:shiwa-architecture}, interaction \texttt{d} on
Figure~\ref{archi:nested}). Ten different child engines can be used by
nested workflows, invoked through a ``submission service'' (step
\texttt{2}, interaction \texttt{d}). Each of these engines can submit
jobs and transfer data to a distributed computing infrastructure (DCI,
step \texttt{3}, interactions \texttt{b} and \texttt{c$_2$}).

Nested workflows
are also often used implicitly to wrap scripts as black-boxes while
these scripts actually correspond to complete workflows.

@@

\begin{figure*}
\centering
\includegraphics[width=1.5\columnwidth]{figures/shiwa-science-gateway.pdf}
\caption{Nested workflow execution through SHIWA Science Gateway
  (Figure reproduced from~\cite{terstyanszky2014enabling} with
  permission of the first author).}
\label{fig:shiwa-architecture}
\end{figure*}

@@

See Figure~\ref{archi:import}. This is an abstract model that we
instantiate with the service invocation architecture for
consistency. Workflows are integrated in the science gateway through
format conversion from a native format to the science gateway
format. This was implemented in the SHIWA Science Gateway through
the IWIR language that provided a common language for portability
across grid workflow
systems~\cite{plankensteiner-prodan-etal:2013}.

@@

\paragraph{Scalability} As in the service architecture, adding a new
workflow instance requires manual configuration in the science gateway
(instance of a parent engine), or in the parent engine (instance of a
child engine) (\texttt{S$_1$=1}). Similarly, elastic engines are
difficult to achieve (\texttt{S$_2$=1}). Distributed engines are
possible, through meta-workflows (\texttt{S$_3$=0}). Task scheduling
is more complex than in other architectures though, due to the fact
that workflow execution is split in different engines (\texttt{S$_4$=1}).
\subsection{Workflow import with service invocation}
